Reading Notes

### 2020-08-13 2pd.tex
messing around trying to get figure to not be bad

%% <history>
Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting. 
The first OPV was created by Tang in 1986 and \cite{Tang1986b} used a bilyaer structure containing copper phthalocyanine and a perylene derivitive. 
This early device had a PCE of 0.95\%.
In 1992, Saricifti and Heeger\cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
Most recently, non-fullerene acceptors (NFAs), like 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.
\begin{wrapfigure}{L}{0.5\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
    \label{fig:itic}
\end{wrapfigure}
The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
VOTCA uses an xml file to do this:
\lstinputlisting[breaklines]{hexane.xml}
It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is backmapped.
VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
\begin{lstlisting}
hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function %%<link to grits> is a three-site hexane model A-B-A, same as VOTCA.
The mapping here is specified as a list of bead name / smarts string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a terminal carbon by including that it has three attached hydrogens (C[H3]).
The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. %%<show overlay>

>>>>

%% <history>
Inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, and their production causes other environmental issues, so they aren't the best solution for solar energy harvesting. 
The first OPV was created by Tang in 1986 and \cite{Tang1986b} used a bilyaer structure containing copper phthalocyanine and a perylene derivitive. 
This early device had a PCE of 0.95\%.
In 1992, Saricifti and Heeger\cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
Most recently, non-fullerene acceptors (NFAs), like 3,9-bis(2-methylene-(3-(1,1-dicyanomethylene)-indanone))-5,5,11,11-tetrakis(4-hexylphenyl)-dithieno[2,3-d:2’,3’-d’]-s-indaceno[1,2-b:5,6-b’]dithiophene (ITIC), are contributing to the PCE increase of modern OPVs \cite{S.Gurney2019}.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
    \label{fig:itic}
\end{wrapfigure}

The planar acceptor-donor-acceptor moeity seen in many NFA backbones (see Figure \ref{fig:itic}) may have more efficient exciton splitting, as compared to a fullerene acceptor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
VOTCA uses an xml file to do this:

%%\lstinputlisting[breaklines]{hexane.xml}

%%\begin{wrapfigure}{L}{0.6\textwidth}
%%    \centering
%%    \includegraphics[width=0.5\textwidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
%%    \label{fig:hexanexml}
%%\end{wrapfigure}

It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is backmapped.
VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
\begin{lstlisting}
hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function %%<link to grits> is a three-site hexane model A-B-A, same as VOTCA.
The mapping here is specified as a list of bead name / smarts string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a terminal carbon by including that it has three attached hydrogens (C[H3]).
The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. %%<show overlay>
